### 2011-07-07 doc/theses/vitasek/diplomka.tex
Thesis: in progress

Název práce: Title [accurate translation of the master thesis title in Czech]

@@

Klíčová slova:  [3-5 keywords in Czech]

@@

TODO talk about key definition from \cite{keX}

\begin{itemize}
	\item XML tree
	\item Element, Attribute
	\item ID, IDREF, IDREFS attribute according to specification
	\item XSD keys (compare them to ID attributes)
	\item Key according to Keys for XML
	\item Attribute mapping
	\item ID set
\end{itemize}

@@

TODO talk about FIDAX
To the best of our knowledge, there are no other articles dealing with this problem

@@

@@

TODO what is heuristics (link wise books), what is metaheuristics (we will be using them)
TODO mention things like Taboo search

TODO we will be working with heus striving to do the following: input is a list of AMs, they have their weight, we try to find a non-conflicting subset which maximizes the weight

@@

\nomenclature{CH}{Construction Heuristic} %TODO decide on how to format CH/IH

@@

TODO types of data:
\begin{itemize}
	\item Realistic - TODO talk about all that are used
	\item Artificial - random graphs - TODO talk about their generation
\end{itemize}

@@

>>>>

Název práce: Odvozování integritních omezení v XML % TODO how to translate this correctly?

@@

Klíčová slova:  XML, ID atributy, odvozování

@@

\begin{itemize}
	\item XML tree - from FIDAX or wherever
	\item Element, Attribute
	\item ID, IDREF, IDREFS attribute according to specification
	\item XSD keys (compare them to ID attributes)
	\item Key according to Keys for XML \cite{keX}
	\item Attribute mapping
	\item ID set
\end{itemize}

@@

TODO talk about FIDAX
To the best of our knowledge, there are no other articles dealing with this problem.

@@

TODO define IS rigorously

@@

TODO what is heuristics (link wise books), what is metaheuristics (we will be using them)

TODO mention things like Taboo search (we won't be using them)

TODO we will be working with heuristics striving to do the following: input is a list of AMs, they have their weight, we try to find a non-conflicting subset which maximizes the weight

@@

% TODO can I format things in nomenclature?
\nomenclature{CH}{Construction Heuristic} %TODO decide on how to format CH/IH

@@

TODO types of data:
\begin{itemize}
	\item Realistic 
	\item Artificial
\end{itemize}

\subsection{Realistic data}

TODO talk about all that are used - mention the dataset name, some characteristics (excel sheet)

\subsection{Artificial data}

TODO these are random graphs.
TODO talk about how they are created, about their structure.
TODO talk about some "density".
TODO show a picture, possibly from GraphViz.

@@

TODO we have asked a lot of questions and got the answers, now is the time to summarize, to find some "wisdom".

First of all: if we have the time, it is best to just let the GLPK run. 
We will find the optimum in this way. 
And for many purposes, this is just fine - we need to infer something about the schema, we do it only once, so it doesn't matter that much how long it takes.

Second: if we don't have enough time, we should do XYZ but it might depend on the characteristics of the data.
For realistic (looks like THIS in graph representation) it is best to do A B C.
Whereas, for artificial data (having IJK as their representation) it is best to just do 1 2 3.
